

```{r}
library(tidyverse)
library(leaflet)
library(sf)
library(rgdal) #reads shapefiles
```



```{r}
city <- readOGR("ca-places-boundaries","CA_Places_TIGER2016", stringsAsFactors = FALSE)
city <- spTransform(city, CRS("+proj=longlat +datum=WGS84"))
```

```{r}
city_sf <- st_as_sf(city)
```

```{r}
city_sf_fixed <- 
  city_sf %>%
  filter(LSAD %in% c(25, 43, 57)) %>% #currently not doing anything since all rows are classed as one of these three (city, town, CDP, or Census Designated Place)
  mutate(FILE = paste("City_", NAME, ".txt", sep = ""))
```

I renamed these General Plan text files because they had typos:

City_Chinio_Hills.txt -> City_Chino_Hills.txt
City_Clistoga.txt -> City_Calistoga.txt
City_Coahella.txt -> City_Coachella.txt
City_Filmore.txt -> City_Fillmore.txt
City_Hidden_Hill.txt -> City_Hidden_Hills.txt
City_Hunington_Park.txt -> City_Huntington_Park.txt
City_La_Canada-Flintridge.txt -> City_La_Canada_Flintridge.txt
City_Palo_Verdes_Estates.txt -> City_Palos_Verdes_Estates.txt
City_Placenta.txt -> City_Placentia.txt
City_Rolling__Hills_Estates.txt -> City_Rolling_Hills_Estates.txt
City_Sun_City.txt -> City_Menifee.txt
City_Temucla.txt -> City_Temecula.txt
City_Whitter.txt -> City_Whittier.txt

```{r}

#The following text was updated in the dataframe in order to match the file names. 

city_sf_fixed$FILE <- gsub("Angels", "Angels Camp", city_sf_fixed$FILE)
city_sf_fixed$FILE <- gsub("Gustine", "Gustine City", city_sf_fixed$FILE)
city_sf_fixed$FILE <- gsub("Truckee", "Town of Truckee", city_sf_fixed$FILE)
city_sf_fixed$FILE <- gsub("Tustin", "Tustin Foothills", city_sf_fixed$FILE)
city_sf_fixed$FILE <- gsub("Windsor", "Town of Windsor", city_sf_fixed$FILE)
city_sf_fixed$FILE <- gsub("Yreka", "Yreka City", city_sf_fixed$FILE)
city_sf_fixed$FILE <- gsub("St. ", "Saint ", city_sf_fixed$FILE)
city_sf_fixed$FILE <- gsub(" \\(.*\\)", "", city_sf_fixed$FILE)
city_sf_fixed$FILE <- gsub("ñ", "n", city_sf_fixed$FILE)
city_sf_fixed$FILE <- gsub("-", "_", city_sf_fixed$FILE)
city_sf_fixed$FILE <- gsub("de ", "De ", city_sf_fixed$FILE)
city_sf_fixed$FILE <- gsub(" ", "_", city_sf_fixed$FILE)

```

```{r}
file_names <- 
  read.csv("fileNames.csv")
```


There ended up being six rows with duplicated file names because the following six names had both a city and a census designated place with the same name. They have different geographies however. 

El Cerrito 
Greenfield
Live Oak
Mountain View
Paradise
Rolling Hills 

^Ask Catherine what to do about this


```{r}
city_sf_final <- city_sf_fixed %>% right_join(file_names, by = "FILE")

#n <- city_sf_final %>% filter(is.na(NAME))
```



```{r}
leaflet() %>%
addProviderTiles(providers$CartoDB.Positron) %>%
addPolygons(data = city_sf_final, 
              label = ~FILE,
              color = "#444444",
              weight = 0.5,
              smoothFactor = 0.8,
              opacity = 1.0,
              fillOpacity = 0.5,
              highlightOptions = highlightOptions(color = "white",
                                                  weight = 1,
                                                  bringToFront = TRUE), 
            labelOptions = labelOptions(
                style = list("font-weight" = "normal",
                             padding = "3px 8px"),
                textsize = "10px",
                direction = "auto"))



```

